\documentclass[11pt]{report}
\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{sectsty}
\usepackage{parcolumns}
\usepackage[normalem]{ulem}
%%\usepackage{showframe} % For illustration

% Add reference functionality
\makeatletter
\sectionfont{\ulemheading{\uuline}}
\let\oldsection\section
\newcommand{\s@section}[2][\relax]{\oldsection*{\llap{\rlap{\hspace{\textwidth}\llap{#1}}}#2}}
\makeatother


\usepackage{titlesec}
\usepackage{xcolor}
\newcommand{\mytitle}[1]{\colorbox{gray!40}{\makebox[\dimexpr\columnwidth-2\fboxsep\relax]{\filcenter #1\strut}}}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{\mytitle}
\titlespacing*{\paragraph} {0pt}{3.25ex plus 1ex minus .2ex}{1em}
\subsectionfont{\normalfont\large\itshape\underline}

\title{Application Project - Phase 1}
\author{J Wofford}
\date{September 2018}

\begin{document}
\raggedright

%%\maketitle

\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
      \Large\textbf{Project: UB Room Reservation System}
      
     \vspace*{3\bigskipamount}
      \large\bfseries\textit\bigskip {Juana Wofford 1014901}
      
      \large\textit{CPSC551-Project Fall 18}
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}

\section*{Abstract\hfill [Ref]}
blah, blah, blah

%%end of abstract text
\section*{Problem Statement}
%%end of problem statement text

\paragraph{Relationships and Data Structure}

\section*{Entities}
\subsubsection{Design}
The system is organized by Reservations. 
\begin{itemize}
\item Reservation has a unique identifier, description name, room identifier, person who requested the reservation, service rating and the date and time for request. The creation date and creation time of the reservation is tracked. \item A reservation can be associated with any room for a specific time period.
\item A room is associated with only one active reservation for a finite time period.
\item A room has a description name, room category and room status.
\item The database will store each registered user's full name, password, email, city and state.
\item A user is identified by a unique identifier and user email.
\item A User can be of type of Admin or Normal exclusively.
\item User of type Admin can manage entire system, can access all data and run reports.
\item User of type Normal does not have any privileges of user type Admin.
\item User types of Admin and Normal can register as users, book a reservation, modify a reservation, cancel a reservation and view status of reservations.
\item User of type Normal can send messages to user of type Admin.
\item User of type Normal can rate service and quality of a reservation.
\end{itemize}

Based on the system design requirements, the following entity types are in the Reservation database:
\begin{itemize}
    \item Reservation,  Reservation Service Rating
    \item Room, Room Category, Room Status
    \item Person, User, User Category
\end{itemize}
%%end of entities design

\section*{Data Queries (in English)}
\subsection*{Reservation Information}
\begin{enumerate}
\item How many Active Reservations are there in the system today?
\item How many Cancelled Reservations are there in the system today?
\item What time of day are there the most Booked Reservations?
\item What time of day are there the least Booked Reservations?
\item What User cancels the most Reservations?
\item What user modifies the most Reservations?
\end{enumerate}

\subsection*{Room Information}
\begin{enumerate}
\item What Room is the most requested?
\item What Room is the least requested?
\item What are the Rooms requested by User?
\item What type of Rooms are available for holding more than 5 people?
\end{enumerate}

\subsection*{Miscellaneous}
\begin{enumerate}
\item What are my open Reservation Requests?
\item How many times have I scheduled the 2nd Floor Conference Room?
\item What conference rooms are available at 1pm on September 6?
\item How many tables are in the 3rd Floor Study Room?
\item What Rooms, dates and times are available that have SmartBoards next month?
\end{enumerate}

\paragraph{Application Implementation Architecture}
%%\subsection*{Google Cloud Architecture Application}


\end{document}
